Modelling at-bats in baseball using the generalised Pareto distribution

### 2023-02-16 bibat/examples/baseball/docs/report.qmd
bump version

---
title: "Modelling at-bats in baseball using the generalised Pareto distribution"
subtitle: "A report created using bibat version 0.0.4"
author: "Teddy Groves"
bibliography: bibliography.bib
reference-location: margin
format:
  html: default
  pdf: default
filters:
  - include-code-files
---

>>>>

---
title: "Modelling at-bats in baseball using the generalised Pareto distribution"
subtitle: "A report created using bibat version 0.0.5"
author: "Teddy Groves"
bibliography: bibliography.bib
reference-location: margin
format:
  html: default
  pdf: default
filters:
  - include-code-files
---
